---
title: "Getting started with `{devoirs}`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with `{devoirs}`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is an ordinary Quarto document instrumented with `{devoirs}`. It is intended for instructors or other authors who are creating course materials. If you are reading this in HTML format, there will be interactive elements.

`{devoirs}` is a system for collecting student input and, if desired, providing immediate feedback. A typical use is to provide assignments for students. You can use Quarto in the  ordinary way, compile the quarto source to HTML, then post on a web site as *static* HTML. The "static" means that the document runs entirely in the student browser. 

```{r include=FALSE}
library(devoirs2)
```

The workflow for a student is simple:

1. Open the document and respond to the question or essay prompts. 
2. At any time, press the "submit" button. This will copy out the student responses and paste them, in YAML format, into the student's clipboard.
3. Once on the clipboard, the student can paste the YAML string into whatever "learning management system" the instructor has set up for the purpose. (This can be as simple as a Google Form.)

By default, student's answers are also saved locally in browser storage. This way, each time the student opens the document, his or her previous work will be filled in. (This behavior can be turned off by the author of the quarto/devoirs document.)

The "collect answers" button is created when the `{devoirs}` system is initiated by an R chunk near the start of the Quarto document. Here it is:

```{r echo=FALSE}
# TO DO, add a no local storage option
devoirs_init(clear_cache = FALSE)
# document-wide chunk options
# can be overridden locally in a chunk
knitr::opts_chunk$set(
  devoirs_feedback = TRUE,   # Change to FALSE to suppress feedback
  devoirs_format = "html"    # Change to "pdf" to use non-interactive markdown 
)
```

There are several ways to solicit student input.

1. A multiple-choice format, like this:

```{devoirs_mc}
#| label: example-1
- choices:
    - id: "a"
      choice: "The items can be as long as you like and can even include LaTeX markup like $\\lim_{x \\rightarrow 0} x^2$."
      feedback_message: "Nice"
      correct: true
    - id: "b"
      choice: Another choice.
      correct: false
      feedback_message: "Sorry -- it is too cold there."
    - id: "c"
      choice: "Still another choice."
      feedback_message: "No chance of that!"
```

2. A free-text (essay) editor.

```{devoirs_text}
#| label: example-2
#| multiline: true
You can (optionally) provide some placeholder text that will be ignored by the data collection system and will disappear when the student starts to edit the text box.
```

3. A dropdown style selector, suitable for very short choices, like this one for picking which month the "darling buds" appear. `r devoirs_mc_dropdown(label='Example-3', choices = c("April", "May", "June"), correct = "May")`

4. A free-text entry suitable for a single word or other short text. For instance, which is the first month of the year? `r devoirs_word(id="example-4", placeholder="enter month name", width=6, true_answer="January", devoirs_feedback=TRUE)`.

NEED TO FIX THIS SO THAT THE `devoirs_feedback` argument is more easily specified.

5. A numerical entry whose correct answer can be specified in *value* $\pm$ *precision* format. For example, type $\pi$ to two decimal digits. `r devoirs_num(label="example-5", true_answer=3.14, interval=0.01, placeholder="0.000", width=6, devoirs_feedback=TRUE, points=3)`

* You need to escape backslashes in the YAML, like `$\\sqrt{10}$`.

 


### Question 1

A triangle that features three distinct interior sides of completely unequal linear lengths 
is classified in geometric topology as a/an `r devoirs_mc_dropdown(label="triangle_type", choices=c("equilateral", "isosceles", "scalene"), correct="scalene", points=3)` triangle structure.

Which of these numbers is even: `r devoirs_mc_dropdown(label="even_num", choices=c(1:5), correct=2, points=3)`


### Question 1

Given the curve formula definition $f(x) = x^2$, the area bounded beneath the curve 
over the strict linear boundary interval $[0, 2]$ evaluates approximately to the numerical 
value .



In classical mechanics, velocity ($v$) is formally modeled as the first mathematical 
derivative of position with respect to time, which we denote as the differential formula 
 
Conversely, acceleration ($a$) corresponds directly to the `r devoirs_word(id="accel_ordinal", placeholder="1st, 2nd, etc.", width=10, true_answer="second", devoirs_feedback=TRUE)` 
derivative of position over elapsed time.


### Question 1: State the name of the package used for dynamic report generation in R.

```{devoirs_text}
#| label: answer_package_name
#| multiline: false
#| devoirs_width: 15
Type your single-line answer response here...
```

### Question 2: Explain in your own words how the knitr engine processes chunk options.

```{devoirs_text}
#| label: explanation_essay_box
#| multiline: true
Enter your detailed multi-line paragraph response text here...
```



3. Evaluate my foot:

```{devoirs_mc}
#| label: testing
- choices:
    - id: "a"
      choice: "Hello to all the ships at sea and on the land."
      feedback_message: "Are you new here? and does LaTeX work? $x^2$"
    - id: "b"
      choice: "When in the course of human events it becomes necessary ...."
      correct: true
      feedback_message: "That is more like it: $\\sqrt{x}$"
    - id: "c"
      choice: "This is the winter of our discontent"
      feedback_message: "a la prochiene."
      correct: true
```

---

### 1. Identify the derivative expression of $f(x) = x^2$:

```{devoirs_mc}
#| label: calculus_basics
#| devoirs_format: html
#| devoirs_feedback: true
- choices:
    - id: "a"
      choice: "The basic expression is $2x$"
      feedback_message: "Good job."
      correct: true
    - id: "b"
      choice: "The complete definition matches **$f'(x) = \\lim_{h \\to 0} \\frac{f(x+h) - f(x)}{h}$**"
      correct: false
      feedback_message: "Sorry."
    - id: "c"
      choice: "An alternative calculation formula: $\\int x \\,dx$"
      feedback_message: "Incorrect, this represents an integration operation."
```


Copy of the above.

```{devoirs_mc}
#| label: calculus_basics2
#| devoirs_format: html
#| devoirs_feedback: true
- choices:
    - id: "a"
      choice: "The basic expression is $2x$"
      feedback_message: "Good job."
      correct: true
    - id: "b"
      choice: "The complete definition matches **$f'(x) = \\lim_{h \\to 0} \\frac{f(x+h) - f(x)}{h}$**"
      correct: false
      feedback_message: "Sorry."
    - id: "c"
      choice: "An alternative calculation formula: $\\int x \\,dx$"
      feedback_message: "Incorrect, this represents an integration operation."
```

### 2. Select all expressions that evaluate to an even integer when $x = 2$:

```{devoirs_mc}
#| label: algebra_multi
#| devoirs_format: markdown
#| devoirs_feedback: false
- choices:
    - id: "a"
      choice: "The value matches $x^2$"
      feedback_message: "True enough"
      correct: true
    - id: "b"
      choice: "The value evaluates to $3x + 1$"
      feedback_message: "Not on your life"
    - id: "c"
      choice: "The value yields $5x$"
      feedback_message: "Sorry!"
      correct: true
```

