---
title: "Getting started with `{devoirs}`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with `{devoirs}`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
library(devoirs2)
```

`r devoirs_init()`


* You need to escape backslashes in the YAML, like `$\\sqrt{10}$`.

An example of `devoirs_mc_dropdown()`: `r devoirs_mc_dropdown(label="Spring", choices = c("April", "May", "June"), correct = "May", devoirs_feedback = FALSE)`


### Question 1

A triangle that features three distinct interior sides of completely unequal linear lengths 
is classified in geometric topology as a/an `r devoirs_mc_dropdown(label="triangle_type", choices=c("equilateral", "isosceles", "scalene"), correct="scalene", points=3)` triangle structure.

Which of these numbers is even: `r devoirs_mc_dropdown(label="even_num", choices=c(1:5), correct=2, points=3)`


### Question 1

Given the curve formula definition $f(x) = x^2$, the area bounded beneath the curve 
over the strict linear boundary interval $[0, 2]$ evaluates approximately to the numerical 
value `r devoirs_num(label="integral_area", true_answer=2.667, interval=0.01, placeholder="0.000", width=6, devoirs_feedback=FALSE, points=3)`.



In classical mechanics, velocity ($v$) is formally modeled as the first mathematical 
derivative of position with respect to time, which we denote as the differential formula 
`r devoirs_word(id="velocity_symbol", placeholder="ds/dt", width=6, true_answer="ds/dt", devoirs_feedback=TRUE)`. 
Conversely, acceleration ($a$) corresponds directly to the `r devoirs_word(id="accel_ordinal", placeholder="1st, 2nd, etc.", width=10, true_answer="second", devoirs_feedback=TRUE)` 
derivative of position over elapsed time.


### Question 1: State the name of the package used for dynamic report generation in R.

```{devoirs_text}
#| label: answer_package_name
#| multiline: false
#| devoirs_width: 15
Type your single-line answer response here...
```

### Question 2: Explain in your own words how the knitr engine processes chunk options.

```{devoirs_text}
#| label: explanation_essay_box
#| multiline: true
Enter your detailed multi-line paragraph response text here...
```



3. Evaluate my foot:

```{devoirs_mc}
#| label: testing
- choices:
    - id: "a"
      choice: "Hello to all the ships at sea and on the land."
      feedback_message: "Are you new here? and does LaTeX work? $x^2$"
    - id: "b"
      choice: "When in the course of human events it becomes necessary ...."
      correct: true
      feedback_message: "That is more like it: $\\sqrt{x}$"
    - id: "c"
      choice: "This is the winter of our discontent"
      feedback_message: "a la prochiene."
      correct: true
```

---

### 1. Identify the derivative expression of $f(x) = x^2$:

```{devoirs_mc}
#| label: calculus_basics
#| devoirs_format: html
#| devoirs_feedback: true
- choices:
    - id: "a"
      choice: "The basic expression is $2x$"
      feedback_message: "Good job."
      correct: true
    - id: "b"
      choice: "The complete definition matches **$f'(x) = \\lim_{h \\to 0} \\frac{f(x+h) - f(x)}{h}$**"
      correct: false
      feedback_message: "Sorry."
    - id: "c"
      choice: "An alternative calculation formula: $\\int x \\,dx$"
      feedback_message: "Incorrect, this represents an integration operation."
```


Copy of the above.

```{devoirs_mc}
#| label: calculus_basics2
#| devoirs_format: html
#| devoirs_feedback: true
- choices:
    - id: "a"
      choice: "The basic expression is $2x$"
      feedback_message: "Good job."
      correct: true
    - id: "b"
      choice: "The complete definition matches **$f'(x) = \\lim_{h \\to 0} \\frac{f(x+h) - f(x)}{h}$**"
      correct: false
      feedback_message: "Sorry."
    - id: "c"
      choice: "An alternative calculation formula: $\\int x \\,dx$"
      feedback_message: "Incorrect, this represents an integration operation."
```

### 2. Select all expressions that evaluate to an even integer when $x = 2$:

```{devoirs_mc}
#| label: algebra_multi
#| devoirs_format: markdown
#| devoirs_feedback: false
- choices:
    - id: "a"
      choice: "The value matches $x^2$"
      feedback_message: "True enough"
      correct: true
    - id: "b"
      choice: "The value evaluates to $3x + 1$"
      feedback_message: "Not on your life"
    - id: "c"
      choice: "The value yields $5x$"
      feedback_message: "Sorry!"
      correct: true
```




