---
title: "Getting started with `{devoirs}`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with `{devoirs}`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is an ordinary Quarto document instrumented with `{devoirs}`. It is intended for instructors or other authors who are creating course materials. If you are reading this in HTML format, there will be interactive elements.

`{devoirs}` is a system for collecting student input and, if desired, providing immediate feedback. A typical use is to provide assignments for students. You can use Quarto in the  ordinary way, compile the quarto source to HTML, then post on a web site as *static* HTML. The "static" means that the document runs entirely in the student browser. 

```{r include=FALSE}
library(devoirs2)
```

The workflow for a student is simple:

1. Open the document and respond to the question or essay prompts. 
2. At any time, press the "submit" button. This will copy out the student responses and paste them, in YAML format, into the student's clipboard.
3. Once on the clipboard, the student can paste the YAML string into whatever "learning management system" the instructor has set up for the purpose. (This can be as simple as a Google Form.)

By default, student's answers are also saved locally in browser storage. This way, each time the student opens the document, his or her previous work will be filled in. (This behavior can be turned off by the author of the quarto/devoirs document.)

The "collect answers" button is created when the `{devoirs}` system is initiated by an R chunk near the start of the Quarto document. Here it is:



## An example {#sec-five-examples}

This is a document with five question prompts, each with a different format.

```{r echo=FALSE}
# TO DO, add a no local storage option
devoirs_init(clear_cache = FALSE)
# document-wide chunk options
# can be overridden locally in a chunk
knitr::opts_chunk$set(
  devoirs_feedback = TRUE,   # Change to FALSE to suppress feedback
  devoirs_format = "html"    # Change to "pdf" to use non-interactive markdown 
)
```

1. A multiple-choice format, like this:

Which planets do humans live on? (Select all that apply.)

```{devoirs_mc}
#| label: example-1
#| points: 5
- choices:
    - id: "a"
      choice: "Earth"
      feedback_message: "Yes, the blue-green ball."
      correct: true
    - id: "b"
      choice: "Venus"
      feedback_message: "Sorry -- it is too hot there. \\(x^3\\)"
    - id: "c"
      choice: "Mars"
      correct: true
      feedback_message: "At least in the imaginations of some very rich people."
```

2. A free-text (essay) editor.

```{devoirs_text}
#| label: example-2
#| multiline: false
What`s your opinion?
```

3. A dropdown style selector, suitable for very short choices, like this one for picking which month the "darling buds" appear. `r devoirs_mc_dropdown(label='Example-3', choices = c("April", "May", "June"), correct = "May")`

4. A free-text entry suitable for a single word or other short text. For instance, which is the first month of the year? `r devoirs_word(id="example-4", placeholder="month name", width=6, true_answer="January")`.

NEED TO FIX THIS SO THAT THE `devoirs_feedback` argument is more easily specified.

5. A numerical entry whose correct answer can be specified in *value* $\pm$ *precision* format. For example, type $\pi$ to two decimal digits. `r devoirs_num(label="example-5", true_answer=3.14, interval=0.01, placeholder="0.000", width=6, devoirs_feedback=TRUE, points=3)`

## Initializing a `{devoirs}` document

Before any `{devoirs}` items such as in @sec-five-examples can be created, you need some boilerplate: two r chunks:

````{verbatim, lang="r"}

```{r include=FALSE}
library(devoirs2)
```

```{r echo=FALSE}
# TO DO, add a no local storage option
devoirs_init(clear_cache = FALSE)
# document-wide chunk options
knitr::opts_chunk$set(
  devoirs_feedback = TRUE,   # Change to FALSE to suppress feedback
  devoirs_format = "html"    # Change to "pdf" to use non-interactive markdown 
)
```

````

The `devoirs_init()` call produces the collect-answers button.

## Creating `{devoirs}` items

The first example in the example is created with a `devoirs_mc` knitr chunk:

````{verbatim, lang = "yaml"}
Which planets do humans live on? (Select all that apply.)

```{devoirs_mc}
#| label: Example-1
#| points: 5
- choices:
    - id: "a"
      choice: "Earth"
      feedback_message: "Yes, the blue-green ball."
      correct: true
    - id: "b"
      choice: "Venus"
      feedback_message: "Sorry -- it is too hot there."
    - id: "c"
      choice: "Mars"
      correct: true
      feedback_message: "At least in the imaginations of some very rich people."
```
````

## Feedback

The examples above, except the text editing block, are operating with immediate feedback to the user. This can be turned on or off at the author's discretion. The behavior is controlled by the `devoirs_feedback` knitr-option, which you can set like this:

`knitr::opts_chunk$set(devoirs_feedback = TRUE)`

A value of `FALSE` turns off the feedback. You can use the same argument (e.g. `devoirs_feedback = TRUE`) as an argument


## Details

* You need to escape backslashes in the YAML, like `$\\sqrt{10}$`.

## Architecture of `{devoirs}` items

Each of the five types of widgets above is a style of user interface that lets the reader specify some information: which of the multiple-choice options is selected, the text of an essay box, a number, a word (or other short string). We'll call this, for each individual widget, the **user input**. The user input to a widget is used for two purposes:

1. To produce immediate feedback to the user if the feedback is turned on. More about that in @sec-feedback.

2. As the record to be included in the collection YAML string that the student will upload for instructor review.

For the instructor to make sense of any widget's user input, that input needs to be identified: Which question is it an answer to.  The identification is in two pieces:

a. The collection YAML string always has a document field giving the name of the source document containing the document.

b. Each individual widget in the document has a **label** that the author needs to ensure is unique to that document. (You can use the same labels in different documents, but don't duplicate a label in one document.)

1. If feedback is turned on, the user input causes the display of feedback to show whether the input was correct or not. (For essays, there's no immediate feedback available. Maybe someday.) This might take the form of a message, a check-vs-x icon, color of the widget, and so on.

2. Storing the input for later **collection** and for updating the browser's local state.

Let's focus for now on the collection. 

